{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-08-28 documents/safety.tex
a

While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was irreplaceable during this. It's like a mirror to an alternate universe where literature made sense.}

>>>>

While from which epidemiological data could be derived.\footnote{The cloud service [scite.ai] was useful during this review.}
